### 2024-08-30 manuscript.tex
Flip map
Cyclonic days distribution

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/map_fig.png}
\caption{
\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern},
RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer},
and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island)
analysed here. The tracks cover Antarctic sectors south of South America, the
Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010 to 2021.
The dotted and dashed lines at 40°S and 55°S delineate the Southern
Ocean area of our analysis and its partitioning into two subsets, respectively.
A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens,
Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
\emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala
CL51 installation at the Macquarie Island station (© Jeﬀ Aquilina, Bureau of
Meteorology).
% TODO: Ask for photo permission and info about license.
}
\label{fig:map}
\end{figure}

@@

@@

The radiation calculations were done in such a way that they always represent
averages of daily means. This is done in order to be consistent with the CERES
SYN1deg data, which are expressed as daily means. Therefore, for every
instantaneous profile in the simulated lidar data is assigned a daily mean
radiation value corresonding to theo the day (in UTC). In turn, the average
radiation during the entire voyage or station measurement is calculated as the
average of the profile values. In the observed lidar data, the daily mean
radiation value is taken from the spatially and temporally co-located CERES
SYN1deg data for the day (in UTC). The voyage or station measurement average
is calculated in the same way.

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/map_fig.pdf}
\caption{
\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern},
RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer},
and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island)
analysed here. The tracks cover Antarctic sectors south of South America, the
Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010 to 2021.
The dotted and dashed lines at 40°S and 55°S delineate the Southern
Ocean area of our analysis and its partitioning into two subsets, respectively.
A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens,
Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
\emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala
CL51 installation at the Macquarie Island station (© Jeﬀ Aquilina, Bureau of
Meteorology).
% TODO: Ask for photo permission and info about license.
}
\label{fig:map}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/cyc_dist.pdf}
\caption{
Geographical distribution of cyclonic days in \textbf{(a)} ERA5 in years
2010--2013 and \textbf{(b)} ICON in model years 2021--2023 (free running) as
identified by CyTRACK, expressed as a fraction of the number of days with
cyclonic activity, defined as grid points located within a double radius of any
cyclone on a given day (UTC).
}
\label{fig:lts}
\end{figure}

@@

The radiation calculations were done in such a way that they always represent
averages of daily means. This is done in order to be consistent with the CERES
SYN1deg data, which are expressed as daily means. Therefore, for every
instantaneous profile in the simulated lidar data is assigned a daily mean
radiation value corresonding to the day (in the Coordinated Universal Time;
UTC). In turn, the average radiation during the entire voyage or station
measurement is calculated as the average of the profile values. In the observed
lidar data, the daily mean radiation value is taken from the spatially and
temporally co-located CERES SYN1deg data for the day (in UTC). The voyage or
station measurement average is calculated in the same way.
